### 2024-02-08 docs/projects/noj/ml.qmd
Noj -rerendered

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7855     -0.2024      0.0281      0.2007      0.6159

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.8316     0.3045     6.0143     0.0000 ***
sepal-width         0.6567     0.0798     8.2255     0.0000 ***
petal-length        0.6798     0.0680     9.9990     0.0000 ***
petal-width        -0.4501     0.1530    -2.9415     0.0041 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.2950 on 96 degrees of freedom
Multiple R-squared: 0.8767,    Adjusted R-squared: 0.8728
F-statistic: 227.5000 on 4 and 96 DF,  p-value: 1.726e-43

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8148     -0.2402      0.0173      0.1886      0.7180

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.0188     0.3171     6.3667     0.0000 ***
sepal-width         0.6187     0.0852     7.2590     0.0000 ***
petal-length        0.6704     0.0716     9.3627     0.0000 ***
petal-width        -0.5103     0.1616    -3.1572     0.0021 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3191 on 96 degrees of freedom
Multiple R-squared: 0.8440,    Adjusted R-squared: 0.8391
F-statistic: 173.0879 on 4 and 96 DF,  p-value: 1.363e-38
